Time Series Modeling of Varying Complexity Captures Subdiffusive Solute Dynamics and Predicts Long Timescale Behavior in Nanoscale Pores.

### 2019-11-26 Ben_Manuscripts/stochastic_transport/Draft.tex
Updates to figures + captions

  %BJC4: another way to visualize data
  %BJC4: I think these are kind of hard to read. Can't really see any trends. Open to other
  %ideas.
  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{1mode_radar.pdf}
  \caption{}\label{fig:1mode_radar}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{2mode_radar.pdf}
  \caption{}\label{fig:2mode_radar}
  \end{subfigure}
  \caption{Another way to visualize Tables~\ref{table:sfbm_params} and~\ref{table:sfbm_params_2mode}}\label{fig:radars}
  \end{figure}

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{1mode_radar_nolines.pdf}
  \caption{}\label{fig:1mode_radar}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{2mode_radar_nolines.png}   % for some reason it has trouble saving this as a PDF
  \caption{}\label{fig:2mode_radar}
  \end{subfigure}
  \caption{Same as Figure~\ref{fig:radars} but with no lines between points}\label{fig:radars_nolines}
  \end{figure}

@@

>>>>

  %BJC4: another way to visualize data
  %BJC4: I think these are kind of hard to read. Can't really see any trends.
  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{1mode_radar.pdf}
  \caption{}\label{fig:1mode_radar}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{2mode_radar.pdf}
  \caption{}\label{fig:2mode_radar}
  \end{subfigure}
  \caption{Another way to visualize Tables~\ref{table:sfbm_params} and~\ref{table:sfbm_params_2mode}}\label{fig:radars}
  \end{figure}

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{1mode_radar_nolines.pdf}
  \caption{}\label{fig:1mode_radar}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{2mode_radar_nolines.eps}   % for some reason it has trouble saving this as a PDF (.eps doesn't show opacity)
  \caption{}\label{fig:2mode_radar}
  \end{subfigure}
  \caption{Same as Figure~\ref{fig:radars} but with no lines between points}\label{fig:radars_nolines}
  \end{figure}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{1mode_AD_hops.pdf}
  \caption{$\mathcal{N}(\sigma) / L(\sigma, \alpha_h)$}\label{fig:1mode_AD_hops}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{1mode_AD_dwells.pdf}
  \caption{$P(\alpha_d) / P_T(\alpha_d, \lambda)$}\label{fig:1mode_AD_dwells}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{hurst_barchart.pdf}
  \caption{$\gamma(H)$}\label{fig:hurst_barchart}
  \end{subfigure}
  \caption{The parameters of the 1 mode model reveal differences in solute
	  dynamics. (a) We parameterized Gaussian ($\mathcal{N}(\sigma)$,
	  parameters given by bars with white background) and L\'evy stable
	  ($L(\sigma, \alpha_h)$, parameters given by bars with gray
	  background) distributions to describe solute hop lengths. We assume
	  the mean ($\mu$) to be zero for these distributions and there to be
	  no skewness ($\beta=0$) in the L\'evy stable distributions. High
	  values of $\sigma$ and lower values of $\alpha_h$ result in larger
	  hops. (b) We parameterized a pure power law ($P(\alpha_d)$, white
	  background) and a truncated power law ($P_T(\alpha_d, \lambda)$, gray
	  background) distribution to describe solute dwell times. Lower values
	  of $\alpha_d$ lead to heavier power law tails and higher values of
	  $\lambda$ truncate the distribution at lower dwell times.(c) Finally,
	  we parameterized the hop autocorrelation function ($\gamma(H)$) to
	  describe the degree of correlation between hops.  Higher values of
	  $H$ display closer to Brownian behavior.
	  }\label{fig:1mode_bar_charts}
  \end{figure}

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{2mode_AD_hops.pdf}
  \caption{$\mathcal{N}(\sigma) / L(\sigma, \alpha_h)$}\label{fig:2mode_AD_hops}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{2mode_AD_dwells.pdf}
  \caption{$P(\alpha_d) / P_T(\alpha_d, \lambda)$}\label{fig:2mode_AD_dwells}
  \end{subfigure}
  \caption{The two mode model parameterizes solute behavior in the pores and
	  tails separately. Mode 1 corresponds to solute behavior within 0.75
	  nm of the pore center, the pore region, and mode 2 corresponds to
	  behavior greater than or equal to 0.75 nm from the pore center, the
	  tail region. (a) Generally, movement is much more restricted in the
	  tail region shown by lower mode 2 $\sigma$ values for the Normal
	  (white background) and L\'evy distributions (gray background). Values
	  of $\alpha$ are significantly lower for urea and acetic acid meaning
	  there is a larger probability that they will take large hops.
	  (b) Dwell times are longer in in the tails. Lower values of
	  $\alpha_d$ correspond to power laws with heavier tails and thus
	  higher probabilities of long dwell times. There is no easily
	  discernable trend in $\lambda$ of the truncated power law
	  distribution (gray background).  Note that we used the same Hurst
	  parameter for both modes due to a low number of sufficiently long
	  sequences of hops in each mode. See Figure~\ref{fig:1mode_bar_charts}
	  for descriptions of the parameters.
  }\label{fig:2mode_bar_charts}
  \end{figure}
